Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-13 doc/JFLA2022/paper.tex
add an explanation in Figure 8
outline for table with stats on packages

\draw[->] (equations) -- (hydras) ;
\draw[->] (mathcomp) -- (gaia) ;
\draw[->] (mathcomp) -- (chains) ;
\draw[->] (paramcoq.south) -- (chains) ;
\draw[->] (pockcc) -- (goedelcc) ;
\end{tikzpicture}
}
\caption{Genealogy and dependencies for \Hydras packages. Dotted boxes represent historical Coq contributions, while straight-line boxes represent maintained Coq packages. Dark grey packages are maintained in the \Hydras GitHub repository, while light grey packages are maintained in other \community repositories.}
  \label{fig:round}
\end{figure}

@@

@@

\fbox{\begin{minipage}[h]{1.0\linewidth}
  Let us prove again the equality $\omega+42+\omega^2= \omega^2$. Let us recall that $\omega^2$ is an abbreviation of $\phi_0(2)$,
\emph{i.e} the third  additive principal ordinal.

>>>>

\draw[->] (equations) -- (hydras) ;
\draw[->] (mathcomp) -- (gaia) ;
\draw[->] (mathcomp) -- (chains) ;
\draw[->] (paramcoq.south) -- (chains) ;
\draw[->] (pockcc) -- (goedelcc) ;
\end{tikzpicture}
}
\caption{Genealogy and dependencies for \Hydras packages. Dotted boxes represent historical Coq contributions, while straight-line boxes represent maintained Coq packages. Dark grey packages are maintained in the \Hydras GitHub repository, while light grey packages are maintained in other \community repositories.}
  \label{fig:genealogy}
\end{figure}

@@

\begin{table}
\centering
\footnotesize
\begin{tabular}{|l|l|l|l|}
\hline
\textbf{Package} & \textbf{Repository} & \textbf{Spec LOC} & \textbf{Proof LOC}\\
\hline
Pocklington & \texttt{pocklington} & & \\
\hline
Goedel & \texttt{goedel} & & \\
\hline
Gaia & \texttt{gaia} & & \\
\hline
Hydra-battles & \texttt{hydra-battles} & & \\
\hline
Addition-chains & \texttt{hydra-battles} & & \\
\hline
Gaia-hydras & \texttt{hydra-battles} & & \\
\hline
\end{tabular}
\caption{Current numbers of lines of code for \Hydras packages.}
\label{tbl:loc}
\end{table}

@@

\fbox{\begin{minipage}[h]{1.0\linewidth}
  Let us prove again the equality $\omega+42+\omega^2= \omega^2$. We recall that $\omega^2$ is an abbreviation of $\phi_0(2)$,
\emph{i.e} the third  additive principal ordinal, and that \texttt{F} is a notation for the coercion which maps natural numbers to ordinals.
